### 2009-04-10 docs/runtime_parameters/runtime_parameters.tex
add the defaults
rp.sh now includes the latex header info to generate the table fixed a typo in previous version updated the tex file to reflect the output of rp.sh
start filling in some descriptions

\renewcommand{\arraystretch}{1.5}
%
% note: list generated via:
% grep namelist probin.f90 | awk '{print ``\\verb= ``, $3, `` = &   &   \\\\"}' | sort

\begin{center}
\begin{longtable}{|l|p{3.0in}|l|}
\caption[runtime parameters]{runtime parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

@@

\verb=  anelastic_cutoff  = &   &   \\
\verb=  base_cutoff_density  = &   &   \\
\verb=  bcx_hi  = &   &   \\
\verb=  bcx_lo  = &   &   \\
\verb=  bcy_hi  = &   &   \\
\verb=  bcy_lo  = &   &   \\
\verb=  bcz_hi  = &   &   \\
\verb=  bcz_lo  = &   &   \\
\verb=  beta_type  = &   &   \\
\verb=  cflfac  = &   &   \\
\verb=  cg_verbose  = &   &   \\
\verb=  check_base_name  = &   &   \\
\verb=  chk_int  = &   &   \\
\verb=  co_latitude  = &   &   \\
\verb=  dm_in  = &   &   \\
\verb=  do_alltoallv  = &   &   \\
\verb=  do_burning  = &   &   \\
\verb=  do_eos_h_above_cutoff  = &   &   \\
\verb=  do_initial_projection  = &   &   \\
\verb=  do_sponge  = &   &   \\
\verb=  dpdt_factor  = &   &   \\
\verb=  drdxfac  = &   &   \\
\verb=  enthalpy_pred_type  = &   &   \\
\verb=  evolve_base_state  = &   &   \\
\verb=  fixed_dt  = &   &   \\
\verb=  grav_const  = &   &   \\
\verb=  hg_bottom_solver  = &   &   \\
\verb=  hg_dense_stencil  = &   &   \\
\verb=  init_divu_iter  = &   &   \\
\verb=  init_iter  = &   &   \\
\verb=  init_shrink  = &   &   \\
\verb=  interp_type_radial_bin_to_cart  = &   &   \\
\verb=  job_name  = &   &   \\
\verb=  lUsingNFiles  = &   &   \\
\verb=  max_dt_growth  = &   &   \\
\verb=  max_grid_size  = &   &   \\
\verb=  max_levs  = &   &   \\
\verb=  max_step  = &   &   \\
\verb=  mg_bottom_solver  = &   &   \\
\verb=  mg_verbose  = &   &   \\
\verb=  min_eff  = &   &   \\
\verb=  min_width  = &   &   \\
\verb=  model_file  = &   &   \\
\verb=  n_cellx  = &   &   \\
\verb=  n_celly  = &   &   \\
\verb=  n_cellz  = &   &   \\
\verb=  nOutFiles  = &   &   \\
\verb=  perturb_model  = &   &   \\
\verb=  plot_base  = &   &   \\
\verb=  plot_base_name  = &   &   \\
\verb=  plot_deltat  = &   &   \\
\verb=  plot_int  = &   &   \\
\verb=  plot_spec  = &   &   \\
\verb=  plot_trac  = &   &   \\
\verb=  pmask_x  = &   &   \\
\verb=  pmask_xyz  = &   &   \\
\verb=  pmask_y  = &   &   \\
\verb=  pmask_z  = &   &   \\
\verb=  prob_hi_x  = &   &   \\
\verb=  prob_hi_y  = &   &   \\
\verb=  prob_hi_z  = &   &   \\
\verb=  prob_lo_x  = &   &   \\
\verb=  prob_lo_y  = &   &   \\
\verb=  prob_lo_z  = &   &   \\
\verb=  radius  = &   &   \\
\verb=  ref_ratio  = &   &   \\
\verb=  regrid_int  = &   &   \\
\verb=  restart  = &   &   \\
\verb=  rotational_frequency  = &   &   \\
\verb=  single_prec_plotfiles  = &   &   \\
\verb=  slope_order  = &   &   \\
\verb=  small_dens  = &   &   \\
\verb=  small_temp  = &   &   \\
\verb=  spherical_in  = &   &   \\
\verb=  sponge_kappa  = &   &   \\
\verb=  stop_time  = &   &   \\
\verb=  temp_diffusion_formulation  = &   &   \\
\verb=  test_set  = &   &   \\
\verb=  the_knapsack_verbosity  = &   &   \\
\verb=  thermal_diffusion_type  = &   &   \\
\verb=  the_sfc_threshold  = &   &   \\
\verb=  use_delta_gamma1_term  = &   &   \\
\verb=  use_divu_firstdt  = &   &   \\
\verb=  use_eos_coulomb  = &   &   \\
\verb=  use_etarho  = &   &   \\
\verb=  use_ppm  = &   &   \\
\verb=  use_soundspeed_firstdt  = &   &   \\
\verb=  use_tfromp  = &   &   \\
\verb=  use_thermal_diffusion  = &   &   \\
\verb=  velpert_amplitude  = &   &   \\
\verb=  velpert_radius  = &   &   \\
\verb=  velpert_scale  = &   &   \\
\verb=  velpert_steep  = &   &   \\
\verb=  verbose  = &   &   \\
\verb=  w0mac_interp_type  = &   &   \\
\verb=  xrb_pert_factor  = &   &   \\
\verb=  xrb_pert_size  = &   &   \\
\verb=  xrb_pert_type  = &   &   \\
\verb=  xrb_use_bottom_sponge  = &   &   \\

\end{longtable}
\end{center}
%

>>>>

{\small

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{3.25in}|l|}
\caption[runtime parameters]{runtime parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

@@

\verb=  anelastic_cutoff =  &   &  3.e6 \\
\verb=  base_cutoff_density =  &   &  3.e6 \\
\verb=  bcx_hi =  & $+x$ boundary condition (valid values are listed in {\tt  boxlib/bc.f90})  &  SLIP\_WALL \\
\verb=  bcx_lo =  & $-x$ boundary condition  &  SLIP\_WALL \\
\verb=  bcy_hi =  & $+y$ boundary condition  &  SLIP\_WALL \\
\verb=  bcy_lo =  & $-y$ boundary condition  &  SLIP\_WALL \\
\verb=  bcz_hi =  & $+z$ boundary condition  &  SLIP\_WALL \\
\verb=  bcz_lo =  & $-z$ boundary condition  &  SLIP\_WALL \\
\verb=  beta_type =  & what type of coefficient to use inside the velocity divergence constraint.  
                       {\tt beta\_type} = 1 uses $\beta_0$; {\tt beta\_type} = 2 uses $\rho_0$ (anelastic);
                       {\tt beta\_type} = 3 uses 1 (small-scale combustion).  &  1 \\
\verb=  cflfac =  & CFL factor to use in the computation of the advection timestep constraint  &  0.5 \\
\verb=  cg_verbose =  &   &  0 \\
\verb=  check_base_name =  & prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int =  & number of timesteps between writing a checkpoint file  &  \\
\verb=  co_latitude =  &   &  ZERO \\
\verb=  dm_in =  & dimensionality (valid values are 2 or 3)  &  2 \\
\verb=  do_alltoallv =  &   &  .false. \\
\verb=  do_burning =  &   &  .true. \\
\verb=  do_eos_h_above_cutoff =  &   &  .true. \\
\verb=  do_initial_projection =  &   &  \\
\verb=  do_sponge =  &   &  .false. \\
\verb=  dpdt_factor =  &   &  0.0d0 \\
\verb=  drdxfac =  &   &  1 \\
\verb=  enthalpy_pred_type =  &   &  predict\_rhohprime \\
\verb=  evolve_base_state =  &   &  .true. \\
\verb=  fixed_dt =  &   &  -1.0d0 \\
\verb=  grav_const =  &   &  -1.5d10 \\
\verb=  hg_bottom_solver =  &   &  -1 \\
\verb=  hg_dense_stencil =  &   &  .true. \\
\verb=  init_divu_iter =  &   &  4 \\
\verb=  init_iter =  &   &  4 \\
\verb=  init_shrink =  &   &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  &   &  1 \\
\verb=  job_name =  &   &  "" \\
\verb=  lUsingNFiles =  &   &  .true. \\
\verb=  max_dt_growth =  &   &  1.1D0 \\
\verb=  max_grid_size =  &   &  64 \\
\verb=  max_levs =  &   &  1 \\
\verb=  max_step =  &   &  \\
\verb=  mg_bottom_solver =  &   &  -1 \\
\verb=  mg_verbose =  &   &  0 \\
\verb=  min_eff =  &   &  0.7d0 \\
\verb=  min_width =  &   &  16 \\
\verb=  model_file =  &   &  \\
\verb=  n_cellx =  &   &  \\
\verb=  n_celly =  &   &  \\
\verb=  n_cellz =  &   &  \\
\verb=  nOutFiles =  &   &  \\
\verb=  perturb_model =  &   &  .false. \\
\verb=  plot_base =  &   &  \\
\verb=  plot_base_name =  &   &  "plt" \\
\verb=  plot_deltat =  &   &  0.0 \\
\verb=  plot_int =  &   &  \\
\verb=  plot_spec =  &   &  \\
\verb=  plot_trac =  &   &  \\
\verb=  pmask_x =  &   &  .false. \\
\verb=  pmask_y =  &   &  .false. \\
\verb=  pmask_z =  &   &  .false. \\
\verb=  ppm_type =  &   &  0 \\
\verb=  prob_hi_x =  &   &  \\
\verb=  prob_hi_y =  &   &  \\
\verb=  prob_hi_z =  &   &  \\
\verb=  prob_lo_x =  &   &  ZERO \\
\verb=  prob_lo_y =  &   &  ZERO \\
\verb=  prob_lo_z =  &   &  ZERO \\
\verb=  radius =  &   &  0.75d8 \\
\verb=  ref_ratio =  &   &  2 \\
\verb=  regrid_int =  &   &  -1 \\
\verb=  restart =  &   &  \\
\verb=  rotational_frequency =  &   &  ZERO \\
\verb=  single_prec_plotfiles =  &   &  .false. \\
\verb=  slope_order =  &   &  4 \\
\verb=  small_dens =  &   &  1.d-5 \\
\verb=  small_temp =  &   &  5.d6 \\
\verb=  spherical_in =  &   &  0 \\
\verb=  sponge_kappa =  &   &  10.d0 \\
\verb=  stop_time =  &   &  -1.d0 \\
\verb=  temp_diffusion_formulation =  &   &  .false. \\
\verb=  test_set =  &   &  '' \\
\verb=  the_copy_cache_max =  &   &  \\
\verb=  the_knapsack_verbosity =  &   &  .false. \\
\verb=  the_layout_verbosity =  &   &  0 \\
\verb=  thermal_diffusion_type =  &   &  1 \\
\verb=  the_sfc_threshold =  &   &  \\
\verb=  use_delta_gamma1_term =  &   &  .false. \\
\verb=  use_divu_firstdt =  &   &  .false. \\
\verb=  use_eos_coulomb =  &   &  .false. \\
\verb=  use_etarho =  &   &  .true. \\
\verb=  use_soundspeed_firstdt =  &   &  .false. \\
\verb=  use_tfromp =  &   &  .false. \\
\verb=  use_thermal_diffusion =  &   &  .false. \\
\verb=  velpert_amplitude =  &   &  0.d0 \\
\verb=  velpert_radius =  &   &  0.75d8 \\
\verb=  velpert_scale =  &   &  0.8d8 \\
\verb=  velpert_steep =  &   &  1.d0 \\
\verb=  verbose =  &   &  0 \\
\verb=  w0mac_interp_type =  &   &  1 \\
\verb=  xrb_pert_factor =  &   &  1.d-2 \\
\verb=  xrb_pert_size =  &   &  5.0d1 \\
\verb=  xrb_pert_type =  &   &  1 \\
\verb=  xrb_use_bottom_sponge =  &   &  .true. \\

\end{longtable}
\end{center}

} % ends \small

%
